---
title: "2024-2025 ACC Conference Stats"
output:
  pdf_document: default
  html_notebook: default
---

```{r}
install.packages("dplyr")
library(dplyr)
install.packages("tidyr")
library(tidyr)
```

```{r}
acc_stats2425 <- read.csv("/Users/hanabaskin/Downloads/ACC Stats 24-25 - Sheet1.csv")
```

```{r}
head(acc_stats2425)
```

```{r}
#check to see how completeness of the data set
colSums(is.na(acc_stats2425))
```

```{r}
#18 teams represented
unique(acc_stats2425$Team)
```
Guiding Question: How concentrated is conference scoring within each ACC team?

```{r}
#percent of total team points per player

team_scoring_concentration_player <- acc_stats2425 |>
  group_by(Team) |>
  mutate(percent_total_team_points = PTS / sum(PTS) * 100) |>
  select(Player, Team, percent_total_team_points) |>
  arrange(desc(percent_total_team_points))
 
```

```{r}
#top scorer share for each team

top_scoring_concentration_team <- acc_stats2425 |>
 group_by(Team) |>
  mutate(percent_total_team_points = PTS / sum(PTS) * 100) |>
  summarise(top_score_share = max(percent_total_team_points)) |>
  arrange(desc(top_score_share))
```

```{r}
top_scoring_concentration_team
```
Scoring concentration is measured as each player’s share of total team points during conference play. Teams with higher concentration rely more heavily on a small number of players, while teams with lower concentration distribute scoring more evenly across the roster. This table shows the teams that rely most heavily on fewer players to score.

```{r}
#creating a table view
View(team_scoring_concentration_player)
```

```{r}
#adding in which player is the top score sharer for each team
top_score_share_player <- acc_stats2425 |>
 group_by(Team) |>
  mutate(percent_total_team_points = PTS / sum(PTS) * 100) |>
  slice_max(percent_total_team_points, n = 1) |>
  select(Team, Player, percent_total_team_points) |>
  arrange(desc(percent_total_team_points))
```

```{r}
#creating a table view
View(top_score_share_player)
```
```{r}
#top 2 player score sharers for each team
top2_score_share_player <- acc_stats2425 |>
 group_by(Team) |>
  mutate(percent_total_team_points = PTS / sum(PTS) * 100,
         team_top_score = max(percent_total_team_points)
         ) |>
  slice_max(percent_total_team_points, n = 2) |>
  arrange(desc(team_top_score), desc(percent_total_team_points)) |>
  select(Team, Player, percent_total_team_points)
```
```{r}
View(top2_score_share_player)
```

